### 2020-06-30 2020/wada/adaptive_domain_adaptation.tex
correct some errors

We also have two assumptions on the regularity of the activation and the loss functions:
\begin{itemize}
\item $a_k$ is bounded in sense of $\normL{a_k(h)} < M$
\item the loss function is bounded in sense of $l(h,y) < A$ $\forall h \in \Omega + \mathbb{B}(M)$ where $\mathbb{B}(M)=\lbrace x\in \mathbb{R}^{d_{model}} | \normL{x}<M \rbrace$ and $A+B = \lbrace x+ \alpha y  | \alpha \in [0..1], x \in A, y \in B \rbrace$  \fyTodo{why not $l(h,y) < A$ ?}
  $\forall x,y$
\end{itemize}

@@

If we the original version of the residual adapter, with the same assumption in the regularization of the adapter, the bound of the risk of translating out-of-domain is only A (the bound of loss function). By using adaptive version, we reduce A by factor $\frac{\epsilon^k_{insep}+\gamma}{p_0}$ which is small if we choose $p_0$ is high enough, the domains are distant and the classifier is good enough. Furthermore $ \varepsilon^k_{insep} < \varepsilon_{insep} $ which is the minimum of the error expectation over the hypothesis space of the classifier. With a trivial prediction $[\frac{1}{K},..,\frac{1}{K}]$ we have error expectation of 0.5. Therefore, $\varepsilon_{insep} \leq 0.5$, i.e, $\varepsilon^k_{insep} < 0.5$.
\fyTodo{I sort of buy the equations but then so what ? We should may be compare with non-adaptive ?}

>>>>

We also have two assumptions on the regularity of the activation and the loss functions:
\begin{itemize}
\item $a_k$ is bounded in sense of $\normL{a_k(h)} < M$
\item the loss function is bounded in sense of $l(h,y) < A$ $\forall h \in \Omega + \mathbb{B}(M)$ where $\mathbb{B}(M)=\lbrace x\in \mathbb{R}^{d_{model}} | \normL{x}<M \rbrace$ and $A+_{\alpha}B = \lbrace x+ \alpha y  | \alpha \in [0..1], x \in A, y \in B \rbrace$  \fyTodo{why not $l(h,y) < A$ ?}
  $\forall x,y$
\end{itemize}

@@

If we the original version of the residual adapter, with the same assumption in the regularization of the adapter, the bound of the risk of translating out-of-domain is only A (the bound of loss function). By using adaptive version, we reduce A by factor $\frac{p_0}{\epsilon^k_{insep}+\gamma}$ which is high if we choose $p_0$ is high enough, the domains are distant and the classifier is good enough.

Furthermore $ \varepsilon^k_{insep} < \varepsilon_{insep} $ which is the minimum of the error expectation over the hypothesis space of the classifier. With a trivial prediction $[\frac{1}{K},..,\frac{1}{K}]$ we have an error expectation equal to 0.5. Therefore, $\varepsilon_{insep} \leq 0.5$, i.e, $\varepsilon^k_{insep} < 0.5$. In the worst case where domains in the mixture are very close, we are still able to reduce the risk of predicting out-of-domain examples by a factor of 2.
\fyTodo{I sort of buy the equations but then so what ? We should may be compare with non-adaptive ?}
